#for Reddit Challenge 
```{r echo=FALSE}
library(tidyverse)
library(corrplot)
library(Hmisc) 
library(ggplot2)
library(ggcorrplot) 
library(corrr)
```

# Update existing dataframe for policy-level challenge
# ALREADY PROCESSED! DON'T NEED TO RUN THIS BLOCK AGAIN
```{r}
all_df <- readxl::read_xlsx('Files/Reddit_data_2806_July_1.xlsx')
df <- readxl::read_xlsx('Files/Comparison_Policy-level_107.xlsx')
df <- df %>%
  select(c('Hunhui', 'Bret', 'content'))

all_df$`C: Misc` <- df$Hunhui[match(all_df$content, df$content)]
all_df$`C: Misc`[is.na(all_df$`C: Misc`)] <- 0
all_df
writexl::write_xlsx(all_df, 'Files/Reddit_data_2806_policy_update.xlsx')
```

# Make a dataset containing title, content, challenges, and teacher types
```{r}
df <- readxl::read_xlsx('Files/Reddit_data_2806_policy_update.xlsx')
colnames(df)
df <- df %>%
  #left only teachers' challenges and their employment status
  select( c("title", "content", colnames(df)[24:32], "In-service", "Substitue/part-time/temporary/unstable position")) %>%
  filter(`In-service` == 1 | `Substitue/part-time/temporary/unstable position` == 1)
# #change column names
colnames(df) <- c("Title", "Content", "High workload", "Insufficient support", "Communication with parents", "Classroom management", "Planning", "Personal concerns", "Relationships with other teachers", "Instruct", "Policy", "Regular teachers", "Substitute/part-time teachers")

writexl::write_xlsx(df, 'Files/Reddit_data_1250_challenges_with_texts.xlsx')
```

# Filtering and pre-processing data
```{r}
df <- readxl::read_xlsx('Files/Reddit_data_1250_challenges_with_texts.xlsx')
df <- df%>%
  select(-c("Title", "Content"))
#reorder column from individual level to policy level
df <- df[, c(6, 4, 5, 8, 1, 2, 7, 3, 9, 10, 11)]
#check the result
# [1] "Personal concerns"                                "Classroom management"                             "Planning"                                        
# [4] "Instruct"                                         "High workload"                                    "Insufficient support"                            
# [7] "Relationships with other teachers/administrators" "Communication with parents"                       "Policy"                                          
# [10] "Regular teachers"                                "Substitute/part-time teachers"   
print(colnames(df))

#filter dataframe --> a total of 1,250
df_total <- df %>%
  filter(`Regular teachers` == 1 | `Substitute/part-time teachers` == 1) %>%
  select(-c("Regular teachers", "Substitute/part-time teachers"))

#986
df_regular <- df %>%
  filter(`Regular teachers` == 1) %>%
  select(-c("Regular teachers", "Substitute/part-time teachers"))

#264
df_sub <- df %>%
  filter(`Substitute/part-time teachers` == 1) %>%
  select(-c("Regular teachers", "Substitute/part-time teachers"))
```

#Draw graphs
```{r}
#function for computing percentages of each column
#Note: this percentage is computed by dividing the sum of each column by the total number of posts(1250). 
#Note: Some posts have no challenges. I did not filter these "no challenge posts" 
getCount_Percentage <- function(dataframe){
  col_name_list <- colnames(dataframe)
  sum_list <- vector()
  for (x in col_name_list) {
    sum_list <- append(sum_list, sum( dataframe[[x]]) )
  }
  
  df_temp <- data.frame( Challenges = col_name_list, value = sum_list)
  df_temp$Challenges <- factor(df_temp$Challenges, levels = df_temp$Challenges)
  total <- dim(dataframe)[1]
  df_temp <- df_temp %>%
    mutate(percentage = value * 100 / total)
  print(df_temp)
  return(df_temp)
}

df_total %>%
  getCount_Percentage() %>%
  mutate(Category = ifelse(Challenges == 'Personal concerns', 'Personal', 
                    ifelse(Challenges == 'Planning' | Challenges == 'Instruct' | Challenges == 'Classroom management', 'Interpersonal',
                    ifelse(Challenges == 'High workload' | Challenges == 'Insufficient support' | Challenges == 'Relationships with other teachers', 'Institutional',
                    ifelse(Challenges == 'Communication with parents', 'Community',
                    ifelse(Challenges == 'Policy', 'Public policy', 0)))))
  ) %>%
  mutate(Category = factor(Category, levels = unique(Category))) %>% #levels : this is for re-ordering bars
  ggplot(aes(fill=Challenges, y=percentage, x=Category )) + 
    geom_bar(position="stack", stat="identity") +  
    # geom_text(aes(label = Challenges),  position="stack", stat="identity", vjust = 1.5) +
    theme_bw() + 
    theme(
      axis.text.x = element_text(angle = 0, vjust = 0, hjust=0.5), 
      # plot.title = element_text(face = "bold", size = 12), 
      # legend.position = "none", 
      axis.ticks =  element_line(colour = "grey70", size = 0.2),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )+
    labs(y= "Proportion", x = "Challenges frame by Socio-ecology model") 

df_regular_grouped <- df_regular %>%
  getCount_Percentage() %>%
  mutate(Group = 1)

df_sub_grouped <- df_sub %>%
  getCount_Percentage() %>%
  mutate(Group = 2)

df_total_grouped <- rbind(df_regular_grouped, df_sub_grouped) %>%
  mutate(Category = ifelse(Challenges == 'Personal concerns', 'Personal', 
                    ifelse(Challenges == 'Planning' | Challenges == 'Instruct' | Challenges == 'Classroom management', 'Interpersonal',
                    ifelse(Challenges == 'High workload' | Challenges == 'Insufficient support' | Challenges == 'Relationships with other teachers', 'Institutional',
                    ifelse(Challenges == 'Communication with parents', 'Community',
                    ifelse(Challenges == 'Policy', 'Public policy', 0)))))
  ) %>%
  mutate(Category = factor(Category, levels = unique(Category))) #this one is for re-ordering bars
  
ggplot(data=df_total_grouped, aes(fill=Challenges, y=percentage, x=Group)) +
  geom_bar(stat = "identity",
           position = "stack") +
  facet_grid(~ Category) +
  theme_bw() + 
    theme(  
      axis.text.x=element_blank(), #remove x axis labels
      axis.ticks.x=element_blank(), #remove x axis ticks
      # axis.ticks =  element_line(colour = "grey70", size = 0.2),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )+
    labs(y= "Proportion", x = "Teacher of Full-time (left), temporary (right) job position") 

ggsave("Challenge_Comparision.png", width=10, height=6) 

```
# Draw some correlation matrix
# In this section, I filtered out "no challenge posts" because we are trying to find relationships between challenges
```{r} 

#Function to return correlation matrix plot
#Now... asterisks are overlapped with texts...
drawCorrelationMatrix <- function(dataframe, font_size = 1){ 
  dataframe.cor <- cor(dataframe, method='spearman')
  dataframe.p.mat <- cor_pmat(dataframe)
  dataframe.p.mat[1,1] = 1
  dataframe.p.mat[2,2] = 1
  dataframe.p.mat[3,3] = 1  #In order to remove *** of cells in digonal
  dataframe.p.mat[4,4] = 1
  dataframe.p.mat[5,5] = 1
  t <- corrplot(dataframe.cor, p.mat = dataframe.p.mat,   method = 'color',  addgrid.col = 'grey50', addCoef.col = 'black',
                tl.srt = 45, tl.cex=0.6, cl.ratio = 0.2, number.cex = font_size,
                col.lim = c(-1, 1), sig.level = c(0.001, 0.01, 0.05), pch.cex = 1.5,
                insig = 'label_sig', pch.col = 'black', order = 'AOE',col=colorRampPalette(c("blue","white","red"))(200))
  return(t)
}

#filter posts having at least one challenge
df_regular <- df_regular %>%
  filter( !(`Personal concerns` == 0 & Planning == 0 & Instruct == 0 & `Classroom management` == 0 & `High workload` == 0 & `Insufficient support` == 0 &
            `Relationships with other teachers` == 0 & `Communication with parents` == 0 & Policy == 0) )

df_sub <- df_sub %>%
  filter( !(`Personal concerns` == 0 & Planning == 0 & Instruct == 0 & `Classroom management` == 0 & `High workload` == 0 & `Insufficient support` == 0 &
            `Relationships with other teachers` == 0 & `Communication with parents` == 0 & Policy == 0) )

df_regular %>% 
  mutate(Personal = ifelse(`Personal concerns` == 1, 1, 0)) %>%
  mutate(Interpersonal = ifelse( (Planning == 1 | Instruct == 1 | `Classroom management` == 1), 1, 0)) %>%
  mutate(Institutional = ifelse( (`High workload` == 1 | `Insufficient support` == 1 | `Relationships with other teachers` == 1), 1, 0)) %>%
  mutate(Community = ifelse(`Communication with parents`, 1, 0)) %>%
  mutate(`Public policy` = ifelse(Policy == 1, 1, 0)) %>%
  .[,10:14] %>% 
  drawCorrelationMatrix()
 
 

df_sub %>% 
  mutate(Personal = ifelse(`Personal concerns` == 1, 1, 0)) %>%
  mutate(Interpersonal = ifelse(Planning == 1 | Instruct == 1 | `Classroom management` == 1, 1, 0)) %>%
  mutate(Institutional = ifelse(`High workload` == 1 | `Insufficient support` == 1 | `Relationships with other teachers` == 1, 1, 0)) %>%
  mutate(Community = ifelse(`Communication with parents`, 1, 0)) %>%
  mutate(`Public policy` = ifelse(Policy == 1, 1, 0)) %>%
  .[,10:14] %>%
  drawCorrelationMatrix()

```

