# for Reddit Challenges Project

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(corrplot)
library(Hmisc) 
library(ggplot2)
library(ggcorrplot) 
library(corrr)
library(quanteda)
library(quanteda.textplots)
library(tidytext)
library(topicmodels)
library(seriation)
library(viridis)
```

# Update existing dataframe for policy-level challenge
# ALREADY PROCESSED! DON'T NEED TO RUN THIS BLOCK AGAIN

```{r, eval = FALSE}
all_df <- readxl::read_xlsx('Files/Reddit_data_2806_July_1.xlsx')
df <- readxl::read_xlsx('Files/Comparison_Policy-level_107.xlsx')
df <- df %>%
  select(c('Hunhui', 'Bret', 'content'))

all_df$`C: Misc` <- df$Hunhui[match(all_df$content, df$content)]
all_df$`C: Misc`[is.na(all_df$`C: Misc`)] <- 0
all_df
writexl::write_xlsx(all_df, 'Files/Reddit_data_2806_policy_update.xlsx')
```


################################################################################

# Make a dataset containing title, content, challenges, and teacher types

```{r, eval=FALSE}
df <- readxl::read_xlsx('Files/Reddit_data_2806_policy_update.xlsx')
colnames(df)
df <- df %>%
  #left only teachers' challenges and their employment status
  select( c("title", "content", colnames(df)[24:32], "In-service", "Substitue/part-time/temporary/unstable position")) %>%
  filter(`In-service` == 1 | `Substitue/part-time/temporary/unstable position` == 1)
# #change column names
colnames(df) <- c("Title", "Content", "High workload", "Insufficient support", "Communication with parents", "Classroom management", "Planning", "Personal concerns", "Relationships with other teachers", "Instruct", "Policy", "Regular teachers", "Substitute/part-time teachers")

writexl::write_xlsx(df, 'Files/Reddit_data_1250_challenges_with_texts.xlsx')
```

################################################################################











################################################################################
# START HERE
################################################################################

# Filtering and pre-processing data

```{r}
df <- readxl::read_xlsx('Files/Reddit_data_1250_challenges_with_texts.xlsx')
df <- df%>%
  select(-c("Title", "Content"))
#reorder column from individual level to policy level
df <- df[, c(6, 4, 5, 8, 1, 2, 7, 3, 9, 10, 11)]
#check the result
# [1] "Personal concerns"                                "Classroom management"                             "Planning"                                        
# [4] "Instruct"                                         "High workload"                                    "Insufficient support"                            
# [7] "Relationships with other teachers/administrators" "Communication with parents"                       "Policy"                                          
# [10] "Regular teachers"                                "Substitute/part-time teachers"   
print(colnames(df))

#filter dataframe --> a total of 1,250
df_total <- df %>%
  filter(`Regular teachers` == 1 | `Substitute/part-time teachers` == 1) %>%
  select(-c("Regular teachers", "Substitute/part-time teachers"))

#986
df_regular <- df %>%
  filter(`Regular teachers` == 1) %>%
  select(-c("Regular teachers", "Substitute/part-time teachers"))

#264
df_sub <- df %>%
  filter(`Substitute/part-time teachers` == 1) %>%
  select(-c("Regular teachers", "Substitute/part-time teachers"))
```



# Draw graphs

```{r}
#function for computing percentages of each column
#Note: this percentage is computed by dividing the sum of each column by the total number of posts(1250). 
#Note: Some posts have no challenges. I did not filter these "no challenge posts" 
getCount_Percentage <- function(dataframe){
  col_name_list <- colnames(dataframe)
  sum_list <- vector()
  for (x in col_name_list) {
    sum_list <- append(sum_list, sum( dataframe[[x]]) )
  }
  
  df_temp <- data.frame( Challenges = col_name_list, value = sum_list)
  df_temp$Challenges <- factor(df_temp$Challenges, levels = df_temp$Challenges)
  total <- dim(dataframe)[1]
  df_temp <- df_temp %>%
    mutate(percentage = value * 100 / total)
  print(df_temp)
  return(df_temp)
}

df_total_overall <- 
  df_total %>%
  getCount_Percentage() %>%
  mutate(Category = ifelse(Challenges == 'Personal concerns', 'Personal', 
                           ifelse(Challenges == 'Planning' | Challenges == 'Instruct' | Challenges == 'Classroom management', 'Interpersonal',
                                  ifelse(Challenges == 'High workload' | Challenges == 'Insufficient support' | Challenges == 'Relationships with other teachers', 'Institutional',
                                         ifelse(Challenges == 'Communication with parents', 'Community',
                                                ifelse(Challenges == 'Policy', 'Public policy', 0)))))
  ) %>%
  mutate(Group = 1) %>%
  mutate(Category = factor(Category, levels = unique(Category))) #levels : this is for re-ordering bars
```

```{r}
ggplot(df_total_overall, aes(x = Category, y = percentage, fill = Challenges)) + 
  geom_bar(position = "stack", stat = "identity", color = "black") + 
  scale_fill_manual(values = viridis::turbo(9), name = "Challenges:") +
  scale_y_continuous(limits = c(0, 50)) + 
  geom_hline(yintercept = 0) +
  theme_bw() + 
  theme(panel.border = element_blank(),
        panel.grid.major.y = element_line(color = "gray85"),
        panel.grid.minor.y = element_line(color = "gray90"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_text(size = 11, family='serif', 
                                   face = 'bold', color = "black", vjust = 4),
        axis.text.y = element_text(size = 14, family='serif'),
        axis.title = element_text(size = 16, family='serif'),
        legend.title = element_text(size = 14, family='serif', face = 'bold'), 
        legend.text = element_text(size = 10, family='serif'),
        legend.position = 'right',
        legend.background = element_blank(),
        legend.box.background = element_rect(colour='black')
  ) +
  labs(y = "Percentage", x = "Challenges Framed by the Socio-Ecological Model") 
```

```{r}
ggsave("output/challenges-overall.png", width=8, height=4.5)
```



```{r}
df_regular_grouped <- 
  df_regular %>%
  getCount_Percentage() %>%
  mutate(Group = 1)

df_sub_grouped <- df_sub %>%
  getCount_Percentage() %>%
  mutate(Group = 2)

df_total_grouped <- rbind(df_regular_grouped, df_sub_grouped) %>%
  mutate(Category = ifelse(Challenges == 'Personal concerns', 'Personal', 
                    ifelse(Challenges == 'Planning' | Challenges == 'Instruct' | Challenges == 'Classroom management', 'Interpersonal',
                    ifelse(Challenges == 'High workload' | Challenges == 'Insufficient support' | Challenges == 'Relationships with other teachers', 'Institutional',
                    ifelse(Challenges == 'Communication with parents', 'Community',
                    ifelse(Challenges == 'Policy', 'Public policy', 0)))))
  ) %>%
  mutate(Category = factor(Category, levels = unique(Category))) #this one is for re-ordering bars
```

```{r}
ggplot(data = df_total_grouped, 
       aes(x = Group, y = percentage, fill = Challenges)) +
  geom_bar(stat = "identity", position = "stack", color = "black") +
  scale_fill_manual(values = viridis::turbo(9), name = "Challenges:") +
  #scale_x_discrete(expand=expansion(add=1)) +
  scale_y_continuous(limits = c(0, 50)) + 
  geom_hline(yintercept = 0) +
  facet_wrap(~ Category, nrow = 1, strip.position = 'bottom') +
  theme_bw() + 
  theme(panel.border = element_blank(),
        panel.grid.major.y = element_line(color = "gray85"),
        panel.grid.minor.y = element_line(color = "gray90"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 14, family='serif'),
        axis.title = element_text(size = 16, family='serif'),
        strip.background = element_blank(),
        strip.text.x = element_text(size = 11, family='serif', face = 'bold', vjust = 2),
        panel.spacing.x = unit(0, "null"),
        legend.title = element_text(size = 14, family='serif', face = 'bold'), 
        legend.text = element_text(size = 10, family='serif'),
        legend.position = 'right',
        legend.background = element_blank(),
        legend.box.background = element_rect(colour='black')
  ) +
  scale_x_discrete(expand=expand_scale(add = 0.4)) +
  labs(y = "Percentage", x = "Challenges of Full-Time (Left) and Temporary (Right) Teachers")
```

```{r}
ggsave("output/challenges-comparison.png", width=8, height=4.5) 
```



################################################################################

# Draw correlation matrices

In this section, I filtered out "no challenge posts" because we are trying to find relationships between challenges

```{r} 
#Function to return correlation matrix plot
#Now... asterisks are overlapped with texts...
drawCorrelationMatrix <- function(dataframe, font_size = 1){ 
  dataframe.cor <- cor(dataframe, method='spearman')
  dataframe.p.mat <- cor_pmat(dataframe)
  dataframe.p.mat[1,1] = 1
  dataframe.p.mat[2,2] = 1
  dataframe.p.mat[3,3] = 1  #In order to remove *** of cells in digonal
  dataframe.p.mat[4,4] = 1
  dataframe.p.mat[5,5] = 1
  t <- corrplot(dataframe.cor, p.mat = dataframe.p.mat,   method = 'color',  addgrid.col = 'grey50', addCoef.col = 'black',
                tl.srt = 45, tl.cex=0.6, cl.ratio = 0.2, number.cex = font_size,
                col.lim = c(-1, 1), sig.level = c(0.001, 0.01, 0.05), pch.cex = 1.5,
                insig = 'label_sig', pch.col = 'black', order = 'AOE',col=colorRampPalette(c("blue","white","red"))(200))
  return(t)
}

#filter posts having at least one challenge
df_regular <- df_regular %>%
  filter( !(`Personal concerns` == 0 & Planning == 0 & Instruct == 0 & `Classroom management` == 0 & `High workload` == 0 & `Insufficient support` == 0 &
            `Relationships with other teachers` == 0 & `Communication with parents` == 0 & Policy == 0) )

df_sub <- df_sub %>%
  filter( !(`Personal concerns` == 0 & Planning == 0 & Instruct == 0 & `Classroom management` == 0 & `High workload` == 0 & `Insufficient support` == 0 &
            `Relationships with other teachers` == 0 & `Communication with parents` == 0 & Policy == 0) )

df_regular %>% 
  mutate(Personal = ifelse(`Personal concerns` == 1, 1, 0)) %>%
  mutate(Interpersonal = ifelse( (Planning == 1 | Instruct == 1 | `Classroom management` == 1), 1, 0)) %>%
  mutate(Institutional = ifelse( (`High workload` == 1 | `Insufficient support` == 1 | `Relationships with other teachers` == 1), 1, 0)) %>%
  mutate(Community = ifelse(`Communication with parents`, 1, 0)) %>%
  mutate(`Public policy` = ifelse(Policy == 1, 1, 0)) %>%
  .[,10:14] %>% 
  drawCorrelationMatrix()
 
 

df_sub %>% 
  mutate(Personal = ifelse(`Personal concerns` == 1, 1, 0)) %>%
  mutate(Interpersonal = ifelse(Planning == 1 | Instruct == 1 | `Classroom management` == 1, 1, 0)) %>%
  mutate(Institutional = ifelse(`High workload` == 1 | `Insufficient support` == 1 | `Relationships with other teachers` == 1, 1, 0)) %>%
  mutate(Community = ifelse(`Communication with parents`, 1, 0)) %>%
  mutate(`Public policy` = ifelse(Policy == 1, 1, 0)) %>%
  .[,10:14] %>%
  drawCorrelationMatrix()
```





################################################################################

# Draw plot of log odds ratios

Read in the data:

```{r} 
text_df <-
  readxl::read_xlsx('Files/Reddit_data_1250_challenges_with_texts.xlsx') %>%
  filter(`Regular teachers` == 1 | 
           `Substitute/part-time teachers` == 1) %>%
  mutate(type = ifelse(`Regular teachers` == 1,
                       "fulltime", 
                       ifelse(`Substitute/part-time teachers` == 1,
                       "parttime",
                       "unknown")
  ),
  text = paste(Title, Content)
  ) %>%
  select(type, text, Title, Content)
```

## Compare words and topics between full-time and part-time teachers

```{r}
my_extra_stopwords <-
  c("NA", "removed", "deleted", "just", "like")
```

### Topics of full-time teachers

```{r}
corpus_fulltime <-
  text_df %>%
  filter(type == 'fulltime') %>%
  quanteda::corpus(text_field = 'text')

dfm_fulltime <- 
  corpus_fulltime %>%
  quanteda::tokens(
    remove_separators = TRUE,
    remove_punct = TRUE,
    remove_symbols = TRUE,
    remove_numbers = TRUE,
    remove_url = TRUE) %>%
  quanteda::dfm(tolower = TRUE) %>%
  quanteda::dfm_remove(c(my_extra_stopwords,
                 quanteda::stopwords("english")))
#dim(dfm_fulltime)
quanteda::topfeatures(dfm_fulltime, scheme = "docfreq")
```

```{r}
dfm_fulltime %>%
  quanteda.textplots::textplot_wordcloud(
    min_count = 10, 
    random_order = FALSE, 
    rotation = 0.25, 
    color = viridis_pal()(8)
  )
```

```{r}
top_terms_fulltime <-
  quanteda::topfeatures(dfm_fulltime, 
                        scheme = "docfreq",
                        n = length(quanteda::featnames(dfm_fulltime))
  )

top_terms_fulltime_df <-
  tibble::tibble(term = names(top_terms_fulltime), 
                 n_ft = top_terms_fulltime
  ) %>%
  mutate(p_ft = round(100 * n_ft / nrow(dfm_fulltime), 2),
         odds_ft = (n_ft / nrow(dfm_fulltime)) / 
           ((nrow(dfm_fulltime) - n_ft) / nrow(dfm_fulltime))
         )
head(top_terms_fulltime_df)
```

### Topics of part-time teachers

```{r}
corpus_parttime <-
  text_df %>%
  filter(type == 'parttime') %>%
  quanteda::corpus(text_field = 'text')

dfm_parttime <- 
  corpus_parttime %>%
  quanteda::tokens(
    remove_separators = TRUE,
    remove_punct = TRUE,
    remove_symbols = TRUE,
    remove_numbers = TRUE,
    remove_url = TRUE) %>%
  quanteda::dfm(tolower = TRUE) %>%
  quanteda::dfm_remove(c(my_extra_stopwords,
                 quanteda::stopwords("english")))
#dim(dfm_parttime)
```

```{r}
dfm_parttime %>%
  quanteda.textplots::textplot_wordcloud(
    min_count = 10, 
    random_order = FALSE, 
    rotation = 0.25, 
    color = viridis_pal()(8)
  )
```

### Analyze Co-Occurring Terms for Full-Time and Part-Time Teachers

```{r}
top_terms_parttime <-
  quanteda::topfeatures(dfm_parttime, 
                        scheme = "docfreq",
                        n = length(quanteda::featnames(dfm_fulltime))
  )

top_terms_parttime_df <-
  tibble::tibble(term = names(top_terms_parttime), 
                 n_pt = top_terms_parttime
  ) %>%
  mutate(p_pt = round(100 * n_pt / nrow(dfm_parttime), 2),
         odds_pt = (n_pt / nrow(dfm_parttime)) / 
           ((nrow(dfm_parttime) - n_pt) / nrow(dfm_parttime))
         )
```

```{r}
terms_comparison_table <-
  top_terms_fulltime_df %>%
  left_join(top_terms_parttime_df, by = 'term') %>%
  mutate(across(n_ft:odds_pt, coalesce, 0),
         odds_ratio = odds_ft / odds_pt,
         log_odds_ratio = abs(log10(odds_ratio))
         ) %>%
  arrange(-odds_ft)
head(terms_comparison_table)
```
```{r}
terms_plot <- 
terms_comparison_table %>%
  filter(p_ft >= 5 | p_pt >= 5)
```

```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=9}
ggplot(data = terms_comparison_table, 
       mapping = aes(x = p_ft, y = p_pt)) +
  geom_point(alpha = 0.4, 
             size = 15,
             show.legend = TRUE,
             aes(color = log_odds_ratio)) +
  scale_color_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x < 0.5, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), 0.5)),
           1)
  }
  ) +
  ggrepel::geom_label_repel(data = terms_plot,
                            aes(label = term),
                            show.legend = FALSE,
                            size = 6,
                            family = 'serif',
                            check_overlap = TRUE,
                            nudge_x = 0.15,
                            nudge_y = 0.15
  ) +
  #geom_text(aes(label = hashtag), check_overlap = TRUE, nudge_y = 0, nudge_x = 0.0075, size = 7, family = 'serif') +
  geom_abline(color = "red") +
  theme_bw() + 
  xlab("Percentage of Full-Time Teacher Posts with Term") +
  ylab("Percentage of Part-Time Teacher Posts with Term") +
  #xlim(0, 5) +
  #ylim(0, 5) +
  geom_hline(yintercept = 0, color = "black") + 
  geom_vline(xintercept = 0, color = "black") +
  theme(panel.border = element_rect(color = "gray80"),
        panel.grid.major = element_line(color = "gray30"),
        panel.grid.minor = element_line(color = "gray80"),
        axis.title=element_text(size=24, family='serif'),
        axis.text=element_text(size=18, family='serif')
  ) +
  labs(color = 'log odds ratio')
```

```{r, include=FALSE, eval=FALSE}
ggsave("output/term-comparison-scatter-plot.png", width = 8, height = 4.5)
```

### Zoomed-In Plot

```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=9}
ggplot(data = terms_comparison_table, 
       mapping = aes(x = p_ft, y = p_pt)) +
  geom_point(alpha = 0.4, 
             size = 15,
             show.legend = TRUE,
             aes(color = log_odds_ratio)) +
  scale_color_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
    ifelse(x < 0.5, 
           scales::rescale(x,
                           to = to,
                           from = c(min(x, na.rm = TRUE), 0.5)),
           1)
  }
  ) +
  ggrepel::geom_label_repel(data = terms_plot,
                            aes(label = term),
                            show.legend = FALSE,
                            size = 6,
                            family = 'serif',
                            check_overlap = TRUE,
                            nudge_x = 0.15,
                            nudge_y = 0.15
  ) +
  #geom_text(aes(label = hashtag), check_overlap = TRUE, nudge_y = 0, nudge_x = 0.0075, size = 7, family = 'serif') +
  geom_abline(color = "red") +
  theme_bw() + 
  xlab("Percentage of Full-Time Teacher Posts with Term") +
  ylab("Percentage of Part-Time Teacher Posts with Term") +
  xlim(0, 20) +
  ylim(0, 20) +
  geom_hline(yintercept = 0, color = "black") + 
  geom_vline(xintercept = 0, color = "black") +
  theme(panel.border = element_rect(color = "gray80"),
        panel.grid.major = element_line(color = "gray30"),
        panel.grid.minor = element_line(color = "gray80"),
        axis.title=element_text(size=24, family='serif'),
        axis.text=element_text(size=18, family='serif')
  ) +
  labs(color = 'log odds ratio')
```

```{r, include=FALSE, eval=FALSE}
ggsave("output/term-comparison-scatter-plot-zoomed.png", width = 8, height = 4.5)
```

```{r}
top_terms_difference <- 
  terms_plot %>% 
  arrange(desc(log_odds_ratio)) %>% 
  head(100)
write_csv(top_terms_difference, "output/top-terms-difference.csv")
```









### Topics

```{r, include=FALSE}
lda_fulltime <- 
  dfm_fulltime %>% 
  topicmodels::LDA(k = 5, control = list(seed = 10202022))
topics_fulltime <- 
  tidytext::tidy(lda_fulltime, matrix = "beta")

top_terms_fulltime <- 
  topics_fulltime %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta) %>%
  mutate(topic = str_c("FT-", topic))

#top_terms_fulltime$term <- 
#  factor(top_terms_fulltime$term, levels = sort(unique(top_terms_fulltime$term)))
```

```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=9}
top_terms_fulltime %>%
  #mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(x = term, 
             y  = beta, 
             fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = 'fixed') +
  coord_flip() +
  scale_x_discrete(limits = rev(levels(top_terms_fulltime$term))) +
  theme_bw() +
  xlab("Term") +
  ylab("Topic-Word Density") +
  theme(axis.title=element_text(size=28, family='serif'),
        axis.text=element_text(size=16, family='serif')
  )
```

```{r, include=FALSE, eval=FALSE}
ggsave("output/topics-fulltime.png", width = 8, height = 4.5)
```

```{r, include=FALSE}
lda_parttime <- 
  dfm_parttime %>% 
  topicmodels::LDA(k = 5, control = list(seed = 10202022))
topics_parttime <- 
  tidytext::tidy(lda_parttime, matrix = "beta")

top_terms_parttime <- 
  topics_parttime %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta) %>%
  mutate(topic = str_c("PT-", topic))

#top_terms_parttime$term <- 
#  factor(top_terms_parttime$term, levels = sort(unique(top_terms_parttime$term)))
```

```{r, echo=FALSE, warning=FALSE, fig.width=16, fig.height=9}
top_terms_parttime %>%
  #mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(x = term, 
             y  = beta, 
             fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = 'fixed') +
  coord_flip() +
  scale_x_discrete(limits = rev(levels(top_terms_parttime$term))) +
  theme_bw() +
  xlab("Term") +
  ylab("Topic-Word Density") +
  theme(axis.title=element_text(size=28, family='serif'),
        axis.text=element_text(size=16, family='serif')
  )
```

```{r, include=FALSE, eval=FALSE}
ggsave("output/topics-parttime.png", width = 8, height = 4.5)
```

### Compare topics of full-time and part-time teachers

```{r, include=FALSE}
top_terms_fulltime_parttime <-
  top_terms_fulltime %>%
  full_join(top_terms_parttime, by = c("topic", "term", "beta")) %>%
  complete(topic, term, fill = list(beta = 0))

top_terms_fulltime_parttime_matrix <-
  top_terms_fulltime_parttime %>%
  pivot_wider(names_from = topic,
              values_from = beta) %>%
  column_to_rownames('term') %>%
  as.matrix()
  
top_terms_fulltime_parttime_seriation <-  
  top_terms_fulltime_parttime_matrix %>%
  seriation::seriate()

terms_ordered <-
  unique(top_terms_fulltime_parttime$term)[get_order(top_terms_fulltime_parttime_seriation, dim=1)]
topics_ordered <-
  unique(top_terms_fulltime_parttime$topic)[get_order(top_terms_fulltime_parttime_seriation, dim=2)]

top_terms_fulltime_parttime_to_plot <-
  top_terms_fulltime_parttime %>%
  mutate(topic = factor(topic, levels = unique(top_terms_fulltime_parttime$topic)),  # topics_orderedq
         term = factor(term, levels = terms_ordered)
  )
```

```{r, echo=FALSE, fig.width=16, fig.height=12}
ggplot(top_terms_fulltime_parttime_to_plot, aes(x = topic, y = term)) +
        geom_tile(aes(fill = beta), color = 'white', size = 0.2) + 
        scale_fill_viridis(rescaler = function(x, to = c(0, 1), from = NULL) {
                ifelse(x < .010, 
                       scales::rescale(x,
                                       to = to,
                                       from = c(min(x, na.rm = TRUE), .012)), 
                       1)
        }
        ) +
        xlab("Topic") +
        scale_x_discrete(position='bottom') +
        ylab("Term") +
        scale_y_discrete(position='right') +
        theme_bw() +
        theme(axis.title = element_text(size=28, family='serif'),
              axis.text = element_text(size=20, family='serif'),
              legend.title = element_text(size=14, family='serif'), 
              legend.text = element_text(size=14, family='serif'),
              legend.position='left',
              legend.background = element_blank(),
              legend.box.background = element_rect(colour='black'),
              panel.background = element_blank(),
              panel.border = element_blank(),
              panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              plot.background = element_blank()
        ) +
        labs(fill = "Topic-Word Density")
```

```{r, include=FALSE, eval=FALSE}
ggsave("output/topics-fulltime-parttime-questions.png", width = 8, height = 6)
```
